Through the eyes of the teacher

### 2021-02-09 paper_1/paper_1_supplement.Rmd
added excel table AOI long format

## Data collection

@@

For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig. The subjects were divided into groups of four, so the study was conducted on two different sessions. All participants were asked to hold a 10-minute lesson. The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering the questionnaire.

By using mobile eye-trackers, the gaze and behavior of the experts and novices was recorded during the lesson. In addition, the speech and sounds and voices were recorded with an audio recorder installed in the middle of the Lab. Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles. One camera was installed to film the class from the side. Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back. Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.

The lessons recorded on video were coded in a post-hoc procedure with a coding software by previously trained raters. The statistical data have been analyzed by using the program RStudio [Link: https://rstudio.com/].

## Measures

### Questionnaire Data
*Describe how we collect questionnaire data (paper or online). Add some basic information about the structure of the questionnaire.*

The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes. 
The scales on the quality of teaching are a validated questionnaire (@helmke2014unterrichtsdiagnostik). Whereas the scales on the teacher's presence behaviour were derived from the research literature (@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen) and were used in the pilot for the first time.

@@

### Eye-tracking equipment

A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements. The head unit is a measuring device with different sensitive sensors. A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds. Infrared light illuminators support the eye tracking sensors which record the eye orientation. The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second. The scene camera has a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height). The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.

The Tobii Pro Glasses 2 software allows for non-screen based recordings of a participants’ attention while moving in real-world settings. The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video. In order to map multiple recordings to AOIs, it is necessary to import the eye-tracking recordings into the Tobii Pro Analyzer software. Also, it is necessary to create a reference image of the scene in which one wishes to plot the gaze data (i.e. snapshot). Once the snapshot is imported, the gaze recordings of multiple recordings can be mapped to the reference image and analyzed in aggregated form. Tobii Pro does not allow to do AOI based analyses within Pro Lab. Also, the dependency on snapshot reference images makes this approach impractical when working in different settings, i.e. different classrooms with various participants. Finally, mapping gaze to people or any moving objects complicated the analyses further.

### Eye-Tracking Data

# prepare data (selected from questionnaire data)
et.raw.data<-read.table("./data/Aperol_pilot_glasses_raw_fixation_saccades_metrics.tsv", dec=",", sep="\t", header=T)

# calculate GRI

# create a basic table (tibble) using tidyverse functions
et.raw.table <- et.raw.data %>%
  group_by(Participant, Variable) %>%
  summarise("Fixation Number" = Number_of_whole_fixations,
            "Average Duration Fixation" = Average_duration_of_whole_fixations,
            "SE Duration Fixation" = se(Total_duration_of_whole_fixations),
            "TOI length" = TOI,
            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
view(et.raw.table)

### Coding Data

@@

-

@@

@@

@@

### Questionnaire Data
*Start entering descriptives and plots here* Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

>>>>

## Procedure/ Data collection

### Set up

For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig. The subjects were divided into groups of four, so the study was conducted on two different sessions. All participants were asked to hold a 10-minute lesson. The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering questionnaires.

@@

### Questionnaire data

After each mini-lesson, the subjects answered items on the teaching quality using a validated questionnaire ((@helmke2014unterrichtsdiagnostik)) and scales on the teacher's presence behavior. An external observer also completed the questionnaire. In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire.

### Behavioral data

The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab. Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles. One camera was installed to film the class from the side. Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back. Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.

### Eyetracking data

A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants. The head unit is a measuring device with different sensitive sensors. A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds. Infrared light illuminators support the eye tracking sensors which record the eye orientation. The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second. The scene camera has a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height). The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.

## Coding/ Data preparation/ Reliability

### Questionnaire Data

The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes. 
The scales on the quality of teaching are a validated questionnaire (@helmke2014unterrichtsdiagnostik). Whereas the scales on the teacher's presence behavior were derived from the research literature (@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen) and were used in the pilot for the first time.

@@

### Behavioral Data

@@

@@

### Eyetracking Data

The Tobii Pro Lab 2 software was used to analyze the teachers' visual attetion during each mini-lesson. The software allows for non-screen based recordings of a participants’ attention while moving in real-world settings. The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video. In order to map multiple recordings to AOIs, we first imported the eye-tracking recordings into the Tobii Pro Analyzer software. Second, we created dynamic Areas of Interest (AOI) manually to plot the gaze data. Once the AOIs are created, the gaze recordings of multiple recordings can be mapped and analyzed in aggregated form. Tobii Pro does not allow to do AOI based analyses within Pro Lab. So we exported a tsv. file to do further analyses in the software R.

# prepare data (selected from questionnaire data)
et.raw.data<-read.table("./data/Aperol_pilot_glasses_AOI.tsv", dec=",", sep="\t", header=T)

# calculate the GRI

# create a basic table (tibble) using tidyverse functions
et.raw.table <- et.raw.data %>%
  group_by(Participant, Variable) %>%
  summarise("Fixation Number" = Number_of_whole_fixations,
            "Average Duration Fixation" = Average_duration_of_whole_fixations,
            "SE Duration Fixation" = se(Total_duration_of_whole_fixations),
            "TOI length" = TOI,
            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)

view(et.raw.table)

@@

### Questionnaire Data

### Behavioral Data

### Eyetracking Data

@@
